The Impact of Interview Disruptions on Data Quality in Social Surveys

### 2024-11-28 paper/paper.qmd
update paper

# Appendix {.unnumbered}

# Additional data details

# Model details {#sec-model-details}
## Model summary
```{r}
#| label: tbl-summary
#| tbl-cap: "Coefficients from a Bayesian logistic regression model examining factors affecting respondents' understanding during interviews, including interview methods, interference types, and country-level indicators."
#| echo: false
#| warning: false
modelsummary(
  list("Bayesian Logistic Regression" = first_model),
  metrics = c("R2", "RMSE")
)
```
@tbl-summary presents the coefficients from our model analyzing factors that influence response comprehension during interviews. The intercept value, 1.823, represents the baseline level of response comprehension when all other predictors are at their reference or baseline levels. Key variables include "interview_conduct_method9," which has a highly positive coefficient of 81.309, indicating that this particular interview method greatly enhances respondent comprehension. In contrast, factors such as "parent_interference" and "child_interference" exhibit negative coefficients (-1.586 and -0.623 respectively), suggesting that these types of interference are associated with lower levels of understanding during interviews.

>>>>

# Appendix {.unnumbered}
## Data Cleaning Notes
We began by importing the raw dataset using the read.csv() function from base R, with a focus on keeping the process flexible for further manual manipulation. Initially, we removed columns that contained more than 80% missing values to retain only the most relevant information for analysis.

To handle missing data, numeric variables were filled with their median values, while categorical variables were imputed with their mode. This approach aimed to maintain data integrity while minimizing assumptions about the distribution of missing values.

Subsequently, additional data cleaning measures were taken. We removed duplicate entries to ensure uniqueness and eliminated outliers in numeric columns using the Z-score method, retaining only those rows with Z-scores within ±3. This step was important for reducing the influence of extreme data points on subsequent analyses.

To enhance clarity and usability, several column names were renamed to be more descriptive. For example, resundq was renamed to respondent_understood. Additionally, the respondent_understood variable was recoded into a binary form (Understood vs. Not_understood) to simplify future analyses.

To further refine the dataset, we consolidated categories for variables with more than five distinct values, grouping the least frequent values into an "Other" category. The country variable was excluded from this process to preserve its geographic specificity, which was deemed valuable for the analysis.

After cleaning, the dataset was split into training and testing sets in a way that ensured the country variable was well-represented in both. This stratified split preserved regional diversity, which was essential for maintaining representativeness in model training and evaluation.

Lastly, the cleaned dataset was saved in both Parquet and CSV formats for use in future stages of the analysis. This ensured compatibility across different software tools and provided efficient access for future work.

## European Social Survey  Methodology
The European Social Survey (ESS) is a cross-national survey conducted biennially across European countries, aimed at measuring the attitudes, beliefs, and behaviors of European citizens. To ensure data accuracy and quality, the ESS employs rigorous survey methodologies and standardized procedures, ensuring comparability across participating countries and providing a reliable data source for social science research and policymaking (European Social Survey, 2024).

The ESS targets individuals aged 15 and older living in private households across participating European countries, using a carefully designed sampling framework to ensure national representativeness. Countries employ multi-stage probability sampling to select respondents, ensuring that each individual has an equal chance of being selected, thereby minimizing selection bias and enhancing the generalizability of survey results.

To collect the data, the ESS uses trained interviewers to conduct face-to-face interviews. These interviews are conducted in the respondents' native language, ensuring that participants can fully understand the questions being asked. The questionnaires are translated following rigorous standardized guidelines to ensure equivalence across languages and cultures (European Social Survey, 2024). Additionally, questionnaires are pre-tested before the official survey is launched to identify and resolve potential misunderstandings, ensuring consistent understanding among respondents.

During data collection, the ESS implements strict quality control procedures, including systematic interviewer training, ensuring they conduct interviews following standardized techniques to reduce bias and maintain data consistency. To ensure sample representativeness, stratified sampling is used in some countries based on demographic characteristics like age, gender, and region, ensuring sufficient representation of different population groups.

Like many survey research initiatives, the ESS faces challenges related to declining response rates. To mitigate non-response, the ESS requires interviewers to make multiple contact attempts, particularly in cases where initial attempts are unsuccessful, including follow-up visits. To further reduce non-response bias, post-stratification weights are applied to the collected data to adjust for differences between the sample and the overall population.

The survey design of the ESS aims to provide a comprehensive overview of social attitudes while maintaining brevity to minimize respondent fatigue. Most interviews are conducted within a reasonable timeframe to ensure high response quality. The ESS places significant emphasis on accurately capturing every viewpoint, ensuring that the voices of marginalized groups are also adequately represented, which helps policymakers and researchers better understand the dynamics of social attitudes in Europe.

By maintaining strict methodologies regarding sampling frameworks, translation procedures, interviewer training, and addressing non-response bias, the European Social Survey has become a trusted source of social data, providing essential support for research into cross-national comparisons and understanding social attitudes.

##  Ideal Methodology

For studying factors that affect respondent understanding during social surveys, an ideal methodology would involve using data from the **European Social Survey (ESS)**. The goal is to make sure we represent people from different countries across Europe fairly, considering things like age, gender, education, and location, so that our findings are accurate and reflect various social contexts.

**Sampling Method**: We’ll use **stratified random sampling**, which means we’ll group people by country first, and then by characteristics like age, gender, and education within each country. This helps make sure that each group is represented well in the sample, reducing bias and making our findings more generalizable to the whole population.

**Sample Size**: To make sure our analysis is meaningful, we plan to include at least **1,500 participants per country**. For larger and more diverse countries, we may increase this number to properly represent smaller groups.

**Data Collection Approach**: We’ll use a **mixed-method approach** for data collection, including face-to-face interviews and self-completed questionnaires to reach different types of people. Interviews will be conducted by trained local interviewers to prevent language barriers or cultural differences from affecting the data quality. We’ll also use self-administered questionnaires for follow-ups to improve the response rate among harder-to-reach groups, like younger people or those who move around frequently.

**Survey Process and Quality Checks**: Interviewers will use standardized scripts to make sure everyone hears the questions the same way. Surveys will be recorded digitally to make data handling easier and to minimize errors. To avoid any bias, interviewers are trained to read questions in a neutral manner.

**Oversampling Certain Groups**: To better understand specific impacts on comprehension, we will **oversample** some groups, like the elderly or those with lower education levels. This gives us more precise data about these groups, but we will use **weight adjustments** afterward to ensure the final dataset reflects the actual population structure.

**Strategies to Improve Response Rates**: We’ll use several strategies to get as many people as possible to participate:
- **Multi-language Support**: Questionnaires will be available in different languages so that non-native speakers can participate.
- **Follow-up Contact**: We’ll follow up with those who initially refuse or don’t respond, trying at least twice to increase participation.
- **Incentives**: We’ll offer small rewards like gift cards or raffle entries to encourage people to take part.

**Data Analysis and Verification**: Before analyzing, we’ll clean up the dataset, deal with missing values, and make sure demographic information is accurate. We’ll use **statistical adjustments** to correct for any missing data, and weighting will be used to ensure that our data accurately represents the population.

### Budget Breakdown for Survey Implementation

To ensure we collect and analyze quality data, we will allocate the budget as follows:

1. **Survey Design**: $8,000
   - This budget includes designing the questionnaire, translating it into multiple languages, and making sure the questions are clear and unbiased. It also covers interviewer training costs.

2. **Sampling and Recruitment**: $15,000
   - This will go towards sampling costs, including **stratified sampling** to make sure all groups are represented proportionally. It also includes acquiring relevant demographic data for the 23 countries participating in ESS.

3. **Recruiting Respondents**: $30,000
   - This covers contacting participants, managing interviews, and compensating them for follow-ups across the countries.

4. **Incentives**: $20,000
   - Incentives are crucial for getting people to take part, especially those harder to reach. We plan to provide small rewards like gift cards or raffle opportunities to encourage participation.

5. **Data Quality Assurance and Analysis**: $12,000
   - This includes data cleaning, quality checks, and analysis costs. We’ll hire statistical consultants to ensure proper data handling, make sure there are no inconsistencies, and apply adjustments to correct biases.

By using this methodology, we aim to get reliable and fair insights into how well people understand survey questions across different contexts, especially in the diverse societies of Europe.

##Comprehension and Interview Experience Survey*
**Conducted by**: DEZHEN CHEN 
**Contact**: dezhen.chen@mail.utoronto.ca

Thank you for taking part in the Comprehension and Interview Experience Survey. Your feedback is essential in helping us understand how respondents perceive and engage with survey questions, and in improving the quality of interview interactions as well as the overall survey process.

**An example of the survey can be found at this link**: https://docs.google.com/forms/d/1BWPU4vFYpzYnkg1nzvXu9b_P12UOXFKcOh4muV7wVQ0/prefill

As a small gesture of appreciation, all participants will have the opportunity to receive a $200 gift card. Ten respondents will be randomly selected to receive this gift.

Please be assured that your responses will remain completely confidential and anonymous. The data collected will be securely stored and used solely for academic and research purposes, with no personal identifying information attached to your answers.

**Please note:**
* All responses are confidential and will be used for research purposes only.
* This survey will take approximately 10 minutes to complete.
* Your participation is entirely voluntary, and you may withdraw at any time.
* All questions marked with an asterisk (*) are required.
* There are no right or wrong answers; we appreciate your honest opinions.

---

 **Part 1: Interviewer Details**

1. **Interviewer Age**  
   - What is the age of the interviewer?  
   * (Please specify in years)

2. **Interviewer Gender**  
   - What is the gender of the interviewer?  
   * Male  
   * Female

---

**Part 2: Interview Process Information**

3. **Interview Conduct Method**  
   - What was the method used to conduct this interview?  
   * Face-to-face  
   * Telephone  
   * Online video interview  
   * Other

4. **Questionnaire Language**  
   - What language was used during the interview?  
   * (Please specify the language)

5. **Question Clarification**  
   - Did you need clarification on the questions during the interview?  
   * No clarification needed  
   * Minor clarification needed  
   * Moderate clarification needed  
   * Extensive clarification needed  
   * Completely unclear, repeated explanations needed  
   * Other

6. **Respondent Understanding Level**  
   - How well do you think the respondent understood the questions?  
   * Fully understood  
   * Mostly understood  
   * Needed some clarification  
   * Partially understood  
   * Did not understand at all

7. **Respondent Tried Their Best**  
   - Do you think the respondent tried their best to answer the questions?  
   * Very unwilling to answer  
   * Somewhat reluctant  
   * Neutral  
   * Willing to answer  
   * Very willing to answer  
   * Other

---

**Part 3: Interference During Interview**

8. **Interference Presence**  
   - Was there any interference during the interview process?  
   * Yes  
   * No

9. **Partner Interference**  
   - Was there any interference by a partner during the interview?  
   * Yes  
   * No

10. **Child Interference**  
   - Was there any interference by children during the interview?  
   * Yes  
   * No

11. **Parent Interference**  
   - Was there any interference by parents during the interview?  
   * Yes  
   * No

12. **Relative Interference**  
   - Was there any interference by other relatives during the interview?  
   * Yes  
   * No

13. **Non-relative Interference**  
   - Was there any interference by non-relatives during the interview?  
   * Yes  
   * No

14. **Unknown Interference**  
   - Was there any unknown source of interference during the interview?  
   * Yes  
   * No

15. **Interference Not Applicable**  
   - Was interference not applicable during this interview?  
   * Yes  
   * No

---

 **Part 4: Additional Feedback**

16. **Additional Comments**  
   - Do you have any suggestions or feedback regarding the interview process? (open-ended)

17. **Interference Details**  
   - If there was interference, could you please describe it in more detail? (open-ended)

18. **Suggestions for Improvement**  
   - Do you have any suggestions to improve the clarity or format of the questions in this survey? (open-ended)

---

**Thank You Message**

Thank you once again for your participation. Your feedback is invaluable in helping us improve the quality of survey interactions and comprehension. We appreciate your time and effort in completing this survey.

# Model details {#sec-model-details}
## Model summary
```{r}
#| label: tbl-summary
#| tbl-cap: "Coefficients from a Bayesian logistic regression model examining factors affecting respondents' understanding during interviews, including interview methods, interference types, and country-level indicators."
#| echo: false
#| warning: false
modelsummary(
  list("Bayesian Logistic Regression" = first_model),
  metrics = c("R2", "RMSE")
)

```
@tbl-summary presents the coefficients from our model analyzing factors that influence response comprehension during interviews. The intercept value, 1.823, represents the baseline level of response comprehension when all other predictors are at their reference or baseline levels. Key variables include "interview_conduct_method9," which has a highly positive coefficient of 81.309, indicating that this particular interview method greatly enhances respondent comprehension. In contrast, factors such as "parent_interference" and "child_interference" exhibit negative coefficients (-1.586 and -0.623 respectively), suggesting that these types of interference are associated with lower levels of understanding during interviews.
